---
title: "learnitgrid - Rubrics or Assessment Grids for R Documents in GitHub Repos"
author: "Philippe Grosjean (phgrosjean@sciviews.org)"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_caption: true
vignette: >
  %\VignetteIndexEntry{learnitgrid - Rubrics or Assessment Grids for R Documents in GitHub Repos}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The {learnitgrid} package implements an application to ease the correction of projects where students have to complete R scripts, R Markdown or Quarto documents. The correction is done by using evaluation grids (or rubrics).

The application is started with `run_grid()`. You have to provide the directory where the data is stored (with subdirectories for `templates`, `repos` and `corrections`, TODO: detailed explanations of the data structure).

If you do not provide any directory, a small package example is used with `run_grid("")`. No R Markdown document is provided in this example. So, you can only see the evaluation grid, but not the items that are evaluated.

You can also install a larger example dataset in your temporary directory and inspect it to see how you have to organize your data:

```{r install_example, eval=FALSE}
library(learnitgrid)
# Decompress the example dataset in a temporary directory and inspect it
install_grid_example(browse = TRUE)
```

The path to these data is set in the "learnitgrid.data.dir" option. You read it with:

```{r option, eval=FALSE}
getOption("learnitgrid.data.dir")
```

Finally, you start the learnitgrid Shiny application with:

```{r start_app, eval=FALSE}
run_grid()
```

Of course, you are supposed to use it with your own data. The provided examples allow to play with the app and get used to its interface.
